A Framework for Equivalence of Cast Calculi and a new Cast Representation

### 2020-10-11 paper.tex
mbind to mlet

% operators
\newcommand{\mbind}[0]{\ensuremath{\;\gg=\;}}
\newcommand{\mlet}[3]{\ensuremath{
\mathtt{let}\ #1\leftarrow#2\ \mathtt{in}\;#3}}
\newcommand{\mcomp}[0]{\ensuremath{\;>=>\;}}

@@

\todo[inline]{KC: in the next paragraph I cite \cite{breazu1991inheritance}}
Continuations are not the only place where casts can accumulate.
Consider a variant of the above program written in
continuation-passing style.  Here, both functions returns
\lstinline|Bool| so there is no implicit cast in tail position.
% However, the argument \lstinline|k| is wrapped in a cast in each
% recursive call because the type of \lstinline|k| is less precise in
% \lstinline|even?| than it is in \lstinline|odd?|.
However, the argument \lstinline|k| is casted in each
recursive call because the type of \lstinline|k| is less precise in
\lstinline|even?| than it is in \lstinline|odd?|. 
Every time a function is casted we record a pieces of
cast information for the input and another piece for
the output, following the approach in \cite{breazu1991inheritance}
and \cite{Breazu-Tannen:1990vc},
so the space complexity is again linear.
\begin{lstlisting}
(define (even? [n : Int] [k : (-> $\star$ Bool)]) : Bool
  (if (= n 0) (k #t) (odd? (- n 1) k)))
(define (odd? [n : Int] [k : (-> Bool Bool)]) : Bool
  (if (= n 0) (k #f) (even? (- n 1) k)))
\end{lstlisting}
These example programs are adapted from those of \cite{herman2010space}.
We direct readers to their work for more examples and a detailed explanation.

@@

The syntax \error{l} occurs several times in the syntax definition. We shall 
view those nonterminals that have an \error{l} case as error monads.
That is, they raise an error with the error message $l$.
The monadic \texttt{let} is defined as follows:
\[
\begin{array}{rcll}
  (\mlet{x}{r}{e}) & = &
  \begin{cases}
    \error{l} & \text{if } r = \error{l} \\
    [r/x]e & \text{otherwise}
  \end{cases}
    %% (\mlet{x}{(\error{l})}{e}) & = & \error{l} \\
    %% (\mlet{x}{a}{e}) & = & [a/x]e & \text{otherwise} \\ 
\end{array}
\]
In the Agda code we use the monad bind operator instead.
% We use 
% the symbol \mbind{} as the monad bind operator, which is defined as follows:
% \[
% \begin{array}{rcll}
% (\error{l}) \mbind f & = & \error{l} \\
%           a \mbind f & = & f(a)      & \text{otherwise}
% \end{array}
% \]
\todo[inline]{KC: KC, you need to replace all uses of monad bind to let.}

\begin{figure}[tp]
	\fbox{\reducetoR{B}{s}{s}} Transition
	\[
	\begin{array}{rclr}
	\figreduceto{\sexpr{\evar{x}}{E}{K}}{\scont{E(x)}{K}}{}
	\figreduceto{\sexpr{\elam{x}{S}{e}}{E}{K}}{\scont{\vfunc{x}{S}{e}{E}}{K}}{}
	\figreduceto{\sexpr{\eapp{e_1}{e_2}}{E}{K}}{
		\sexpr{e_1}{E}{\Kcons{\FappXO{e_2}{E}}{K}}
	}{}
	\figreduceto{\sexpr{\etrue}{E}{K}}{\scont{\vtrue}{K}}{}
	\figreduceto{\sexpr{\efalse}{E}{K}}{\scont{\vfalse}{K}}{}
	\figreduceto{\sexpr{\eif{e_1}{e_2}{e_3}}{E}{K}}{
		\scont{e_1}{\Kcons{\Fif{e_2}{e_3}{E}}{K}}
	}{}
	\figreduceto{\sexpr{\econs{e_1}{e_2}}{E}{K}}{
		\sexpr{e_1}{E}{\Kcons{\FconsXO{e_2}{E}}{K}}
	}{}
	\figreduceto{\sexpr{\efst{e}}{E}{K}}{\sexpr{e}{E}{\Kcons{\Ffst}{K}}}{}
	\figreduceto{\sexpr{\esnd{e}}{E}{K}}{\sexpr{e}{E}{\Kcons{\Fsnd}{K}}}{}
	\figreducetoH{
		\sexpr{\ecast{e}{\ccast{S}{l}{T}}}{E}{K}
	}{
		\sexpr{e}{E}{\Kcons{\Fcast{\ccast{S}{l}{T}}}{K}}
	}{}
	\figreducetoH{\scont{v}{\Kcons{\Fcast{\ccast{S}{l}{T}}}{K}}}{
		\applyCast{v}{\ccast{S}{l}{T}} \; \mbind \; \lambda u. \scont{u}{K}
	}{}
	\figreduceto{\scont{v_1}{\Kcons{\FappXO{e_2}{E}}{K}}}{\sexpr{e_2}{E}{
			\Kcons{\FappOX{v_1}}{K}}
	}{}
	\figreduceto{\scont{v}{\Kcons{\FappOX{\vfunc{x}{S}{e}{E}}}{K}}}{
		\sexpr{e}{E[x:=v]}{K}
	}{}
	\figreducetoH{\scont{v}{\Kcons{\FappOX{(\vfuncc{u}{S_1}{T_1}{l}{S_2}{T_2})}}{K}}}{
		\scont{v}{
			\Kcons{\Fcast{\ccast{S_2}{\bar{l}}{S_1}}}{
				\Kcons{\FappOX{u}}{
					\Kcons{\Fcast{\ccast{T_1}{l}{T_2}}}{K}}}}
	}{}
	\figreduceto{\scont{\vtrue}{\Kcons{\Fif{e_2}{e_3}{E}}{K}}}{\sexpr{e_2}{E}{K}}{}
	\figreduceto{\scont{\vfalse}{\Kcons{\Fif{e_2}{e_3}{E}}{K}}}{\sexpr{e_3}{E}{K}}{}
	\figreduceto{\scont{v_1}{\Kcons{\FconsXO{e_2}{E}}{K}}}{
		\sexpr{e_2}{E}{\Kcons{\FconsOX{v_1}}{K}}
	}{}
	\figreduceto{\scont{v_2}{\Kcons{\FconsOX{v_1}}{K}}}{
		\scont{\vcons{v_1}{v_2}}{K}
	}{}
	\figreduceto{\scont{\vcons{v_1}{v_2}}{\Kcons{\Ffst}{K}}}{\scont{v_1}{K}}{}
	\figreducetoH{\scont{\vconsc{u}{S_1}{T_1}{l}{S_2}{T_2}}{\Kcons{\Ffst}{K}}}{
		\scont{u}{
			\Kcons{\Ffst}{
				\Kcons{\Fcast{\ccast{S_1}{l}{S_2}}}{K}}}	
	}{}
	\figreduceto{\scont{\vcons{v_1}{v_2}}{\Kcons{\Fsnd}{K}}}{\scont{v_2}{K}}{}
	\figreducetoH{\scont{\vconsc{u}{S_1}{T_1}{l}{S_2}{T_2}}{\Kcons{\Fsnd}{K}}}{
		\scont{u}{
			\Kcons{\Fsnd}{
				\Kcons{\Fcast{\ccast{T_1}{l}{T_2}}}{K}}}	
	}{}
	\figreduceto{\scont{v}{\Knil}}{\shalt{v}}{}
	\end{array}
	\]

@@

	\fbox{$\applyCastName_{\mathtt{\BLUD}}(v,\ccast{S}{l}{T}) = r$}
	\[
	\begin{array}{rclr}
	\applyCastName(v, \ccast{\Tdyn}{l}{\Tdyn}) &=& \just{v} \\
	\applyCastName(v, \ccast{G}{l}{\Tdyn}) &=&
	\just{\vdyn{G}{v}} \\
	\applyCastName(v, \ccast{P}{l}{\Tdyn}) &=&
	\just{\vdyn{G}{\proxy{v}{\ccast{P}{l}{G}}}}
	\\ && \text{if } G \sim P, G \neq P \\  
% 	& \text{if } G \sim P, G \neq P \\  
	\applyCastName(\vdyn{G}{u}, \ccast{\Tdyn}{l}{H}) &=&          
	\project{u}{G}{l}{H}\\
	\applyCastName(\vdyn{G}{u}, \ccast{\Tdyn}{l}{Q}) &=&
	\project{u}{G}{l}{H} \mbind \lambda v. \proxy{v}{\ccast{H}{l}{Q}}
	\\
	&& \text{if } H \sim Q, H \neq Q \\
% 	& \text{if } H \sim Q, H \neq Q \\
	\applyCastName(v, \ccast{P}{l}{Q}) &=&
	\just{\proxy{v}{\ccast{P}{l}{Q}}}
	\\&& \text{if } P \smile Q \\
	\applyCastName(v, \ccast{P}{l}{Q}) &=&
	\error{l}
	\\&& \text{if } P \not\smile Q
	\end{array}
	\]

@@

\begin{definition}[Cast Abstract Data Type (Cast ADT)]
	\label{def:cast-rep}
	A cast abstract data type is a family, namely $Cast$, indexed by two types, 
	with four operators and two properties of operators:
\begin{itemize}
	\item $\id{T}$: create an identity cast
	\item $\compose{c}{c}$: compose two casts
	\item $\translate{\ccast{S}{l}{T}}$: translate a cast in the source 
		program to a $\textit{Cast}_{S,T}$
	\item $\denote{c}(v)$: apply a cast to a value
	\item If $ \valuetyping{v}{T} $ then $\denote{\id{T}}(v)=v$
	\item If $ \valuetyping{v}{T_1} $ and
		$ \casttyping{c}{T_1}{T_2} $ and
		$ \casttyping{d}{T_2}{T_3} $ 
		then 
		$ \denote{\compose{c}{d}}(v) = (\denote{c}(v)\mbind\denote{d})$
\end{itemize}
We use the syntax \casttyping{c}{S}{T} to mean $c$ is in the set 
$\textit{Cast}_{S,T}$.
\end{definition}

@@

\begin{figure}[tp]
	\fbox{\reducetoS{C}{s}{s}} Transition
	\[
	\begin{array}{rclr}
	\figreduceto{\sexpr{\evar{x}}{E}{K}}{\scont{E(x)}{K}}{}
	\figreducetoH{
		\sexpr{\elam{x}{S}{e}}{E}{K}
	}{
		\scont{\ecast{\vfunc{x}{S}{e}{E}}{\Pfunc{id(S)}{id(T)}}}{K}
	}{}
	& &
	\highlight{
	\sidecond{
		\expressiontyping{\Gamma,S}{e}{T}
		\text{ and }
		\Gamma \vdash E}
	}
	\\
	\figreduceto{\sexpr{\eapp{e_1}{e_2}}{E}{K}}{
		\sexpr{e_1}{E}{\mkCont{\Kcons{\FappXO{e_2}{E}}{K}}}
	}{}
	\figreduceto{\sexpr{\etrue}{E}{K}}{\scont{\vtrue}{K}}{}
	\figreduceto{\sexpr{\efalse}{E}{K}}{\scont{\vfalse}{K}}{}
	\figreduceto{\sexpr{\eif{e_1}{e_2}{e_3}}{E}{K}}{
		\sexpr{e_1}{E}{\mkCont{\Kcons{\Fif{e_2}{e_3}{E}}{K}}}
	}{}
	\figreduceto{\sexpr{\econs{e_1}{e_2}}{E}{K}}{
		\sexpr{e_1}{E}{\mkCont{\Kcons{\FconsXO{e_2}{E}}{K}}}
	}{}
	\figreduceto{\sexpr{\efst{e}}{E}{K}}{
		\sexpr{e}{E}{\mkCont{\Kcons{\Ffst}{K}}}
	}{}
	\figreduceto{\sexpr{\esnd{e}}{E}{K}}{
		\sexpr{e}{E}{\mkCont{\Kcons{\Fsnd}{K}}}
	}{}
	\figreducetoH{
		\sexpr{\ecast{e}{\ccast{S}{l}{T}}}{E}{K}
	}{
		\sexpr{e}{E}{\extCont{\translate{\ccast{S}{l}{T}}}{K}}
	}{}
	\figreducetoH{\scont{v}{\Kcons{\Fcast{c}}{k}}}{
		\denote{c}(v) \; \mbind \; \lambda u. \applyCont{u}{K}
	}{}
	\end{array}
	\]

	\fbox{$\applyCont{v}{k}=s$}
	\[
	\begin{array}{rclr}
	\figequalto{\applyCont{v_1}{\Kcons{\FappXO{e_2}{E}}{K}}}{\sexpr{e_2}{E}{
			\mkCont{\Kcons{\FappOX{v_1}}{K}}}
	}{}
	\figequaltoH{
		\applyCont{v}{\Kcons{\FappOX{(\ecast{\vfunc{x}{S}{e}{E}}{\Pfunc{c}{d}})}}{K}}
	}{
		\denote{c}(v) \mbind \lambda u. \
		\sexpr{e}{E[x:=u]}{\extCont{d}{K}}
	}{}
	\figequalto{\applyCont{\vtrue}{\Kcons{\Fif{e_2}{e_3}{E}}{K}}}{\sexpr{e_2}{E}{K}}{}
	\figequalto{\applyCont{\vfalse}{\Kcons{\Fif{e_2}{e_3}{E}}{K}}}{\sexpr{e_3}{E}{K}}{}
	\figequalto{\applyCont{v_1}{\Kcons{\FconsXO{e_2}{E}}{K}}}{
		\sexpr{e_2}{E}{\mkCont{\Kcons{\FconsOX{v_1}}{K}}}
	}{}
	\figequaltoH{\applyCont{v_2}{\Kcons{\FconsOX{v_1}}{K}}}{
		\scont{\ecast{\vcons{v_1}{v_2}}{\Pprod{\id{T_1}}{\id{T_2}}}}{K}
	}{}
	& & 
	\highlight{\sidecond{
%		\casttyping{K}{\Pprod{T_1}{T_2}}{T'}
		\valuetyping{v_1}{T_1}
		\text{ and }
		\valuetyping{v_2}{T_2}
	}}
	\\
	\figequaltoH{
		\applyCont{\ecast{\vcons{v_1}{v_2}}{\Pprod{c_1}{c_2}}}{\Kcons{\Ffst}{K}}
	}{
		\denote{c_1}(v_1) \mbind \lambda u.
		\scont{u}{K}
	}{}
	\figequaltoH{
		\applyCont{\ecast{\vcons{v_1}{v_2}}{\Pprod{c_1}{c_2}}}{\Kcons{\Fsnd}{K}}
	}{
		\denote{c_2}(v_2) \mbind \lambda u.
		\scont{u}{K}
	}{}
	\figequalto{\applyCont{v}{\Knil}}{\shalt{v}}{}
	\end{array}
	\]

@@

\begin{definition}[Lazy UD Cast ADT]
	\label{def:LazyUD-CastADT}
	A Cast is a Lazy UD Cast if:
	\begin{enumerate}
	\item $\denote{\translate{\ccast{\Tdyn}{l}{\Tdyn}}}(v) = v$
	\item $\denote{\translate{\ccast{G}{l}{\Tdyn}}}(v) = \vdyn{G}{v}$
	\item $\denote{\translate{\ccast{P}{l}{\Tdyn}}}(v) = 
		\denote{\translate{\ccast{P}{l}{G}}}(v) \mbind 
		\denote{\ccast{G}{l}{\Tdyn}}$\\
		if $G \sim P$ and $G \neq P$	
	\item $\denote{\translate{\ccast{\Tdyn}{l}{G}}}(\vdyn{G}{u}) = u$
	\item $\denote{\translate{\ccast{\Tdyn}{l}{H}}}(\vdyn{G}{u}) = \error{l}$ \qquad
		if $G \neq H$
	\item $\denote{\translate{\ccast{\Tdyn}{l}{Q}}}(v) = 
		\denote{\translate{\ccast{\Tdyn}{l}{H}}}(v) \mbind
		\denote{\translate{\ccast{H}{l}{Q}}}$\\
		if $H \sim Q$ and $H \neq Q$
	\item $\denote{\translate{\ccast{\Pbool}{l}{\Pbool}}}(v) = v$
		\item 
		$\denote{\translate{\ccast{\Pfunc{S_1}{T_1}}{l}{\Pfunc{S_2}{T_2}}}}(
		\ecast{\vfunc{x}{S}{e}{E}}{\Pfunc{c}{d}})$\\
		$=
		\ecast{\vfunc{x}{S}{e}{E}}{
			\Pfunc{
				(\compose{\translate{\ccast{S_2}{\bar{l}}{S_1}}}{c})}{
				(\compose{d}{\translate{\ccast{T_1}{l}{T_2}}})}}$
		\item 
		$\denote{\translate{\ccast{\Pprod{S_1}{T_1}}{l}{\Pprod{S_2}{T_2}}}}(
		\ecast{\vcons{v_1}{v_2}}{\Pprod{c}{d}})$\\
		$=
		\ecast{\vcons{v_1}{v_2}}{
			\Pprod{
				(\compose{c}{\translate{\ccast{S_1}{l}{S_2}}})}{
				(\compose{d}{\translate{\ccast{T_1}{l}{T_2}}})}}$
		\item $\denote{\translate{\ccast{P}{l}{Q}}}(v) = \error{l}$\qquad
			if $\notshallowlyconsistent{P}{Q}$
	\end{enumerate}
\end{definition}

@@

% \begin{figure}

% \fbox{\bisimc{Z}{c}{S}{T}}
% \begin{gather*}
% \infr{}{\bisimc{[]}{id(T)}{T}{T}} \quad
% \infr{}{\bisimc{[\ccast{S}{l}{T}]}{\translate{\ccast{S}{l}{T}}}{S}{T}}
% \\[1ex]
% \infr{
% 	\bisimc{Z_1}{c_1}{T_1}{T_2}\\
% 	\bisimc{Z_2}{c_2}{T_2}{T_3}
% }{
% 	\bisimc{(Z_1 \mathrm{++} Z_2)}{(\compose{c_1}{c_2})}{T_1}{T_3}
% }
% \end{gather*}

>>>>

% operators
% \newcommand{\mbind}[0]{\ensuremath{\;\gg=\;}}
% \newcommand{\mcomp}[0]{\ensuremath{\;>=>\;}}
\newcommand{\mlet}[3]{\ensuremath{
\mathit{let}\ {#1\leftarrow#2}\ \mathit{in}\;#3}}

@@

\todo[inline]{KC: in the next paragraph I cite \cite{breazu1991inheritance}
and \cite{breazu1990computing}}

Continuations are not the only place where casts can accumulate.
Consider a variant of the above program written in
continuation-passing style.  Here, both functions returns
\lstinline|Bool| so there is no implicit cast in tail position.
% However, the argument \lstinline|k| is wrapped in a cast in each
% recursive call because the type of \lstinline|k| is less precise in
% \lstinline|even?| than it is in \lstinline|odd?|.
However, the argument \lstinline|k| is casted in each
recursive call because the type of \lstinline|k| is less precise in
\lstinline|even?| than it is in \lstinline|odd?|. 
Every time a function is casted we record a pieces of
cast information for the input and another piece for
the output, following the approach in \cite{breazu1991inheritance}
and \cite{breazu1990computing},
so the space complexity is again linear.
\begin{lstlisting}
(define (even? [n : Int] [k : (-> $\star$ Bool)]) : Bool
  (if (= n 0) (k #t) (odd? (- n 1) k)))
(define (odd? [n : Int] [k : (-> Bool Bool)]) : Bool
  (if (= n 0) (k #f) (even? (- n 1) k)))
\end{lstlisting}
These example programs are adapted from those of \cite{herman2010space}.
We direct readers to their work for more examples and a detailed explanation.

@@

The syntax \error{l} occurs several times in the syntax definition. We shall 
view those nonterminals that have an \error{l} case as error monads.
That is, they raise an error with the error message $l$.
The monadic \texttt{let} is defined as follows:
\[
\begin{array}{rcll}
  (\mlet{x}{r}{e}) & = &
  \begin{cases}
    \error{l} & \text{if } r = \error{l} \\
    [r/x]e & \text{otherwise}
  \end{cases}
    %% (\mlet{x}{(\error{l})}{e}) & = & \error{l} \\
    %% (\mlet{x}{a}{e}) & = & [a/x]e & \text{otherwise} \\ 
\end{array}
\]
In the Agda code we use the monad bind operator instead.
% We use 
% the symbol \mbind{} as the monad bind operator, which is defined as follows:
% \[
% \begin{array}{rcll}
% (\error{l}) \mbind f & = & \error{l} \\
%           a \mbind f & = & f(a)      & \text{otherwise}
% \end{array}
% \]

\begin{figure}[tp]
	\fbox{\reducetoR{B}{s}{s}} Transition
	\[
	\begin{array}{rclr}
	\figreduceto{\sexpr{\evar{x}}{E}{K}}{\scont{E(x)}{K}}{}
	\figreduceto{\sexpr{\elam{x}{S}{e}}{E}{K}}{\scont{\vfunc{x}{S}{e}{E}}{K}}{}
	\figreduceto{\sexpr{\eapp{e_1}{e_2}}{E}{K}}{
		\sexpr{e_1}{E}{\Kcons{\FappXO{e_2}{E}}{K}}
	}{}
	\figreduceto{\sexpr{\etrue}{E}{K}}{\scont{\vtrue}{K}}{}
	\figreduceto{\sexpr{\efalse}{E}{K}}{\scont{\vfalse}{K}}{}
	\figreduceto{\sexpr{\eif{e_1}{e_2}{e_3}}{E}{K}}{
		\scont{e_1}{\Kcons{\Fif{e_2}{e_3}{E}}{K}}
	}{}
	\figreduceto{\sexpr{\econs{e_1}{e_2}}{E}{K}}{
		\sexpr{e_1}{E}{\Kcons{\FconsXO{e_2}{E}}{K}}
	}{}
	\figreduceto{\sexpr{\efst{e}}{E}{K}}{\sexpr{e}{E}{\Kcons{\Ffst}{K}}}{}
	\figreduceto{\sexpr{\esnd{e}}{E}{K}}{\sexpr{e}{E}{\Kcons{\Fsnd}{K}}}{}
	\figreducetoH{
		\sexpr{\ecast{e}{\ccast{S}{l}{T}}}{E}{K}
	}{
		\sexpr{e}{E}{\Kcons{\Fcast{\ccast{S}{l}{T}}}{K}}
	}{}
	\figreducetoH{\scont{v}{\Kcons{\Fcast{\ccast{S}{l}{T}}}{K}}}{
	    \mlet{u}{\applyCast{v}{\ccast{S}{l}{T}}}{\scont{u}{K}}
% 		\applyCast{v}{\ccast{S}{l}{T}} \; \mbind \; \lambda u. \scont{u}{K}
	}{}
	\figreduceto{\scont{v_1}{\Kcons{\FappXO{e_2}{E}}{K}}}{\sexpr{e_2}{E}{
			\Kcons{\FappOX{v_1}}{K}}
	}{}
	\figreduceto{\scont{v}{\Kcons{\FappOX{\vfunc{x}{S}{e}{E}}}{K}}}{
		\sexpr{e}{E[x:=v]}{K}
	}{}
	\figreducetoH{\scont{v}{\Kcons{\FappOX{(\vfuncc{u}{S_1}{T_1}{l}{S_2}{T_2})}}{K}}}{
		\scont{v}{
			\Kcons{\Fcast{\ccast{S_2}{\bar{l}}{S_1}}}{
				\Kcons{\FappOX{u}}{
					\Kcons{\Fcast{\ccast{T_1}{l}{T_2}}}{K}}}}
	}{}
	\figreduceto{\scont{\vtrue}{\Kcons{\Fif{e_2}{e_3}{E}}{K}}}{\sexpr{e_2}{E}{K}}{}
	\figreduceto{\scont{\vfalse}{\Kcons{\Fif{e_2}{e_3}{E}}{K}}}{\sexpr{e_3}{E}{K}}{}
	\figreduceto{\scont{v_1}{\Kcons{\FconsXO{e_2}{E}}{K}}}{
		\sexpr{e_2}{E}{\Kcons{\FconsOX{v_1}}{K}}
	}{}
	\figreduceto{\scont{v_2}{\Kcons{\FconsOX{v_1}}{K}}}{
		\scont{\vcons{v_1}{v_2}}{K}
	}{}
	\figreduceto{\scont{\vcons{v_1}{v_2}}{\Kcons{\Ffst}{K}}}{\scont{v_1}{K}}{}
	\figreducetoH{\scont{\vconsc{u}{S_1}{T_1}{l}{S_2}{T_2}}{\Kcons{\Ffst}{K}}}{
		\scont{u}{
			\Kcons{\Ffst}{
				\Kcons{\Fcast{\ccast{S_1}{l}{S_2}}}{K}}}	
	}{}
	\figreduceto{\scont{\vcons{v_1}{v_2}}{\Kcons{\Fsnd}{K}}}{\scont{v_2}{K}}{}
	\figreducetoH{\scont{\vconsc{u}{S_1}{T_1}{l}{S_2}{T_2}}{\Kcons{\Fsnd}{K}}}{
		\scont{u}{
			\Kcons{\Fsnd}{
				\Kcons{\Fcast{\ccast{T_1}{l}{T_2}}}{K}}}	
	}{}
	\figreduceto{\scont{v}{\Knil}}{\shalt{v}}{}
	\end{array}
	\]

@@

	\fbox{$\applyCastName_{\mathtt{\BLUD}}(v,\ccast{S}{l}{T}) = r$}
	\[
	\begin{array}{rclr}
	\applyCastName(v, \ccast{\Tdyn}{l}{\Tdyn}) &=& \just{v} \\
	\applyCastName(v, \ccast{G}{l}{\Tdyn}) &=&
	\just{\vdyn{G}{v}} \\
	\applyCastName(v, \ccast{P}{l}{\Tdyn}) &=&
	\just{\vdyn{G}{\proxy{v}{\ccast{P}{l}{G}}}}
	\\ && \text{if } G \sim P, G \neq P \\  
% 	& \text{if } G \sim P, G \neq P \\  
	\applyCastName(\vdyn{G}{u}, \ccast{\Tdyn}{l}{H}) &=&          
	\project{u}{G}{l}{H}\\
	\applyCastName(\vdyn{G}{u}, \ccast{\Tdyn}{l}{Q}) &=&
	\mlet{v}{\project{u}{G}{l}{H}}{\proxy{v}{\ccast{H}{l}{Q}}}
% 	\project{u}{G}{l}{H} \mbind \lambda v. \proxy{v}{\ccast{H}{l}{Q}}
	\\
	&& \text{if } H \sim Q, H \neq Q \\
% 	& \text{if } H \sim Q, H \neq Q \\
	\applyCastName(v, \ccast{P}{l}{Q}) &=&
	\just{\proxy{v}{\ccast{P}{l}{Q}}}
	\\&& \text{if } P \smile Q \\
	\applyCastName(v, \ccast{P}{l}{Q}) &=&
	\error{l}
	\\&& \text{if } P \not\smile Q
	\end{array}
	\]

@@

\begin{definition}[Cast Abstract Data Type (Cast ADT)]
	\label{def:cast-rep}
	A cast abstract data type is a family, namely $Cast$, indexed by two types, 
	with four operators and two properties of operators:
\begin{itemize}
	\item $\id{T}$: create an identity cast
	\item $\compose{c}{c}$: compose two casts
	\item $\translate{\ccast{S}{l}{T}}$: translate a cast in the source 
		program to a $\textit{Cast}_{S,T}$
	\item $\denote{c}(v)$: apply a cast to a value
	\item If $ \valuetyping{v}{T} $ then $\denote{\id{T}}(v)=v$
	\item If $ \valuetyping{v}{T_1} $ and
		$ \casttyping{c}{T_1}{T_2} $ and
		$ \casttyping{d}{T_2}{T_3} $ 
		then 
% 		$ \denote{\compose{c}{d}}(v) = (\denote{c}(v)\mbind\denote{d})$
        $ \denote{\compose{c}{d}}(v) = \mlet{v}{\denote{c}(v)}{\denote{d}(v)}$
\end{itemize}
We use the syntax \casttyping{c}{S}{T} to mean $c$ is in the set 
$\textit{Cast}_{S,T}$.
\end{definition}

@@

\begin{figure}[tp]
	\fbox{\reducetoS{C}{s}{s}} Transition
	\[
	\begin{array}{rclr}
	\figreduceto{\sexpr{\evar{x}}{E}{K}}{\scont{E(x)}{K}}{}
	\figreducetoH{
		\sexpr{\elam{x}{S}{e}}{E}{K}
	}{
		\scont{\ecast{\vfunc{x}{S}{e}{E}}{\Pfunc{\id{S}}{\id{T}}}}{K}
	}{}
	& &
	\highlight{
	\sidecond{
		\expressiontyping{\Gamma,S}{e}{T}
		\text{ and }
		\Gamma \vdash E}
	}
	\\
	\figreduceto{\sexpr{\eapp{e_1}{e_2}}{E}{K}}{
		\sexpr{e_1}{E}{\mkCont{\Kcons{\FappXO{e_2}{E}}{K}}}
	}{}
	\figreduceto{\sexpr{\etrue}{E}{K}}{\scont{\vtrue}{K}}{}
	\figreduceto{\sexpr{\efalse}{E}{K}}{\scont{\vfalse}{K}}{}
	\figreduceto{\sexpr{\eif{e_1}{e_2}{e_3}}{E}{K}}{
		\sexpr{e_1}{E}{\mkCont{\Kcons{\Fif{e_2}{e_3}{E}}{K}}}
	}{}
	\figreduceto{\sexpr{\econs{e_1}{e_2}}{E}{K}}{
		\sexpr{e_1}{E}{\mkCont{\Kcons{\FconsXO{e_2}{E}}{K}}}
	}{}
	\figreduceto{\sexpr{\efst{e}}{E}{K}}{
		\sexpr{e}{E}{\mkCont{\Kcons{\Ffst}{K}}}
	}{}
	\figreduceto{\sexpr{\esnd{e}}{E}{K}}{
		\sexpr{e}{E}{\mkCont{\Kcons{\Fsnd}{K}}}
	}{}
	\figreducetoH{
		\sexpr{\ecast{e}{\ccast{S}{l}{T}}}{E}{K}
	}{
		\sexpr{e}{E}{\extCont{\translate{\ccast{S}{l}{T}}}{K}}
	}{}
	\figreducetoH{\scont{v}{\Kcons{\Fcast{c}}{k}}}{
	    \mlet{u}{\denote{c}(v)}{\applyCont{u}{K}}
% 		\denote{c}(v) \; \mbind \; \lambda u. \applyCont{u}{K}
	}{}
	\end{array}
	\]

	\fbox{$\applyCont{v}{k}=s$}
	\[
	\begin{array}{rclr}
	\figequalto{\applyCont{v_1}{\Kcons{\FappXO{e_2}{E}}{K}}}{\sexpr{e_2}{E}{
			\mkCont{\Kcons{\FappOX{v_1}}{K}}}
	}{}
	\figequaltoH{
		\applyCont{v}{\Kcons{\FappOX{(\ecast{\vfunc{x}{S}{e}{E}}{\Pfunc{c}{d}})}}{K}}
	}{
	    \mlet{u}{\denote{c}(v)}{\sexpr{e}{E[x:=u]}{\extCont{d}{K}}}
% 		\denote{c}(v) \mbind \lambda u. \
% 		\sexpr{e}{E[x:=u]}{\extCont{d}{K}}
	}{}
	\figequalto{\applyCont{\vtrue}{\Kcons{\Fif{e_2}{e_3}{E}}{K}}}{\sexpr{e_2}{E}{K}}{}
	\figequalto{\applyCont{\vfalse}{\Kcons{\Fif{e_2}{e_3}{E}}{K}}}{\sexpr{e_3}{E}{K}}{}
	\figequalto{\applyCont{v_1}{\Kcons{\FconsXO{e_2}{E}}{K}}}{
		\sexpr{e_2}{E}{\mkCont{\Kcons{\FconsOX{v_1}}{K}}}
	}{}
	\figequaltoH{\applyCont{v_2}{\Kcons{\FconsOX{v_1}}{K}}}{
		\scont{\ecast{\vcons{v_1}{v_2}}{\Pprod{\id{T_1}}{\id{T_2}}}}{K}
	}{}
	& & 
	\highlight{\sidecond{
%		\casttyping{K}{\Pprod{T_1}{T_2}}{T'}
		\valuetyping{v_1}{T_1}
		\text{ and }
		\valuetyping{v_2}{T_2}
	}}
	\\
	\figequaltoH{
		\applyCont{\ecast{\vcons{v_1}{v_2}}{\Pprod{c_1}{c_2}}}{\Kcons{\Ffst}{K}}
	}{
	    \mlet{u}{\denote{c_1}(v_1)}{\scont{u}{K}}
% 		\denote{c_1}(v_1) \mbind \lambda u.
% 		\scont{u}{K}
	}{}
	\figequaltoH{
		\applyCont{\ecast{\vcons{v_1}{v_2}}{\Pprod{c_1}{c_2}}}{\Kcons{\Fsnd}{K}}
	}{
	    \mlet{u}{\denote{c_2}(v_2)}{\scont{u}{K}}
% 		\denote{c_2}(v_2) \mbind \lambda u.
% 		\scont{u}{K}
	}{}
	\figequalto{\applyCont{v}{\Knil}}{\shalt{v}}{}
	\end{array}
	\]

@@

\begin{definition}[Lazy UD Cast ADT]
	\label{def:LazyUD-CastADT}
	A Cast is a Lazy UD Cast if:
	\begin{enumerate}
	\item $\denote{\translate{\ccast{\Tdyn}{l}{\Tdyn}}}(v) = v$
	\item $\denote{\translate{\ccast{G}{l}{\Tdyn}}}(v) = \vdyn{G}{v}$
	\item $\denote{\translate{\ccast{P}{l}{\Tdyn}}}(v) = 
	    \mlet{v}{\denote{\translate{\ccast{P}{l}{G}}}(v)}{\denote{\ccast{G}{l}{\Tdyn}}(v)}
% 		\denote{\translate{\ccast{P}{l}{G}}}(v) \mbind 
% 		\denote{\ccast{G}{l}{\Tdyn}}
        $\\
		if $G \sim P$ and $G \neq P$	
	\item $\denote{\translate{\ccast{\Tdyn}{l}{G}}}(\vdyn{G}{u}) = u$
	\item $\denote{\translate{\ccast{\Tdyn}{l}{H}}}(\vdyn{G}{u}) = \error{l}$ \qquad
		if $G \neq H$
	\item $\denote{\translate{\ccast{\Tdyn}{l}{Q}}}(v) = 
	    \mlet{v}{\denote{\translate{\ccast{\Tdyn}{l}{H}}}(v)}{\denote{\translate{\ccast{H}{l}{Q}}}(v)}
% 		\denote{\translate{\ccast{\Tdyn}{l}{H}}}(v) \mbind
% 		\denote{\translate{\ccast{H}{l}{Q}}}
		$\\
		if $H \sim Q$ and $H \neq Q$
	\item $\denote{\translate{\ccast{\Pbool}{l}{\Pbool}}}(v) = v$
		\item 
		$\denote{\translate{\ccast{\Pfunc{S_1}{T_1}}{l}{\Pfunc{S_2}{T_2}}}}(
		\ecast{\vfunc{x}{S}{e}{E}}{\Pfunc{c}{d}})$\\
		$=
		\ecast{\vfunc{x}{S}{e}{E}}{
			\Pfunc{
				(\compose{\translate{\ccast{S_2}{\bar{l}}{S_1}}}{c})}{
				(\compose{d}{\translate{\ccast{T_1}{l}{T_2}}})}}$
		\item 
		$\denote{\translate{\ccast{\Pprod{S_1}{T_1}}{l}{\Pprod{S_2}{T_2}}}}(
		\ecast{\vcons{v_1}{v_2}}{\Pprod{c}{d}})$\\
		$=
		\ecast{\vcons{v_1}{v_2}}{
			\Pprod{
				(\compose{c}{\translate{\ccast{S_1}{l}{S_2}}})}{
				(\compose{d}{\translate{\ccast{T_1}{l}{T_2}}})}}$
		\item $\denote{\translate{\ccast{P}{l}{Q}}}(v) = \error{l}$\qquad
			if $\notshallowlyconsistent{P}{Q}$
	\end{enumerate}
\end{definition}

@@
